Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-05-01 text/back_end_KS.qmd
methods smoothing

**Analyses**. Analyses are simultaneously descriptive and spatial. We answer RQ1 by producing Geomarket-level tables and graphs that show how the Geomarkets in a selected metropolitan area vary on racial and socioeconomic characteristics and how they vary over time. For example, in the San Francisco Bay Area, how does the City of Oakland Geomarket (CA07) differ from the Alameda County Exluding Oakland Geomarket (CA08). We also produce interactive maps at the census tract-level to show more granular variation within and between Geomarkets.

We answer RQ2 by analyzing student list purchases that encompassed all Geomarkets in a selected metropolitan areas. Descriptive tables and graphs describe the racial and socioeconomic characteristics of prospects that would have been included/excluded had the purchase filtered on particular Geomarkets. Interactive maps provide a more granual visualization of where prospects lived and went to high school. For example, for purchased profiles who lived in the Chester County Geomarket (PA02) \[OR PHILADELPHIA PA05\] and identified as Black, where in the county did these students live and which high schools did they attend?

@@

>>>>

**Analyses**. Analyses are simultaneously descriptive and spatial. We answer RQ1 by producing Geomarket-level tables and graphs that show how the Geomarkets in a selected metropolitan area vary on racial and socioeconomic characteristics and how they vary over time. We also produce interactive maps at the census tract-level to show more granular variation within and between Geomarkets.

We answer RQ2 by analyzing student list purchases that encompassed all Geomarkets in a selected metropolitan areas. Descriptive tables and graphs describe the racial and socioeconomic characteristics of prospects that would have been included/excluded had the purchase filtered on particular Geomarkets. We also create interactive maps of prospect pools by Geomarket contributions to provide a more granular visualization of analyses.

```{=html}

<!-- [DO WE NEED THIS LEVEL OF DETAIL???]

For example, for purchased profiles who lived in the Chester County Geomarket (PA02) [OR PHILADELPHIA PA05] and identified as Black, where in the county did these students live and which high schools did they attend?

 For example, for purchased profiles who lived in the Chester County Geomarket (PA02) [OR PHILADELPHIA PA05] and identified as Black, where in the county did these students live and which high schools did they attend?

@@

-->
```
